---
title: "Quiz 1"
output: html_notebook
---

## loading the dataset:
```{r}
data <- read.table(unz("quiz1_data.zip", "hw1_data.csv"), header=TRUE, sep=",")
```

The names of the columns:
```{r}
colnames(data)
```
First two rows of the dataset:
```{r}
data[1:2, ]
```
Number of rows in the dataset:
```{r}
nrow(data)
```
last two rows of the data:
```{r}
tail(data, 2)
````
Value of `Ozone` in the 47th row:
```{r}
data[47, "Ozone"]
```
Number of missing values in `Ozone` column:
```{r}
sum(is.na(data$Ozone))
```
mean of `Ozone` column:
```{r}
mean(data$Ozone, na.rm=TRUE)
```
Extract the subset of rows of the data frame where Ozone values are above 31 and Temp values are above 90. What is the mean of Solar.R in this subset?
```{r}
sub_data <- data[data$Ozone > 31 & data$Temp > 90,]
mean(sub_data$Solar.R, na.rm = TRUE)
```
What is the mean of "Temp" when "Month" is equal to 6? 
```{r}
sub_data <- data[data$Month == 6, ]
mean(sub_data$Temp, na.rm = TRUE)
```

What was the maximum ozone value in the month of May (i.e. Month is equal to 5)?
```{r}
sub_data <- data[data$Month == 5, ]
max(sub_data$Ozone, na.rm = TRUE)
```

